A Road Segment Prioritization Approach for Cycling Infrastructure

### 2023-04-24 README.Rmd
Tighten up prose around choice of Manchester

Funding alone is therefore no guarantee of a change in
commuting across the country; it must be used to design adequate cycling
infrastructure that is based on motivators and deterrents to cycling. In this paper we 
propose an approach for planning a connected cycling network that is meant to 
be applicable to any city (as shown in the Appendix), and we use the city of Manchester as a case study. Greater 
Manchester aims to become the first region to reach a carbon neutral transport network; 
its local authorities have developed plans for a 1800 mile walking and cycling network 
(Bee Network) that will be delivered over 10 years [@manchestercyclingbee2020]. While schemes 
have already been put in place for around a quarter of this network, the majority is yet to be built.

>>>>

Funding alone is therefore no guarantee of a change in
commuting across the country; it must be used to design adequate cycling
infrastructure that is based on motivators and deterrents to cycling. In this paper we 
propose an approach for planning connected cycling networks that can be generalised to any city with appropriate input data (as shown in the Appendix).
We used the city of Manchester as a case study due to its ambitions to become the first UK region with a carbon neutral transport network, supported by ambitious plans for a 1800 mile walking and cycling network 
(the 'Bee Network') that will be delivered over 10 years [@manchestercyclingbee2020]. While schemes 
have already been put in place for around a quarter of this network, the majority is yet to be built.
